Estimating individual subjective values of emotion regulation strategies

### 2022-03-03 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex
everything works now
knitted document

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Subjective values of emotion regulation strategies}
\keywords{emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis\newline\indent Word count: X}
\usepackage{lineno}

@@

\abstract{
Individuals have a repertoire of emotion regulation (ER) strategies at their disposal, which they can use more or less flexibly.
In ER flexibility research, strategies that facilitate goal achievement are considered adaptive and therefore are subjectively valuable.
Individuals are motivated to reduce their emotional arousal effectively and to avoid cognitive effort.
Perceived costs of ER strategies in the form of effort, however, are highly subjective.
Subjective values (SVs) should therefore represent a trade-off between effectiveness and subjectively required cognitive effort.
However, SVs of ER strategies have not been determined so far.
We present a paradigm that is suitable for determining individual SVs of ER strategies.
Using a multilevel modelling approach, it will be investigated whether individual SVs can be explained by effectiveness (subjective arousal, facial muscle activity) and subjective effort.
Relations of SVs to personality traits will be explored
}

@@

Every day we are confronted with stressful or emotionally demanding situations.
The ability to modify emotional experiences, expressions, and physiological reactions\textsuperscript{1} to regulate emotions is an important cognitive skill.
It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning.\textsuperscript{2}
Different strategies can be used to regulate emotions, namely situation selection, situation modification, attentional deployment, cognitive change, and response modification,\textsuperscript{1} and, following the taxonomy of Powers and LaBar,\textsuperscript{3} individuals can implement ER strategies by means of different tactics.
So called antecedent-focused strategies, e.g., attentional deployment and cognitive change, take effect early in the emotion generation process.\textsuperscript{1}
In contrast, response modification takes place late in the process and is therefore conceptualized as a response-focused strategy.\textsuperscript{1}
This postulated temporal sequence of ER strategies influences their effectiveness.
It is meta-analytically proven that all mentioned strategies reduce subjective emotional arousal.\textsuperscript{4}
Distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed small to medium effect sizes on measures of emotional experience (distraction: \emph{d\textsubscript{+}} = 0.27; suppression: \emph{d\textsubscript{+}} = 0.27).
Distancing as tactic of cognitive change showed the highest effectiveness with an effect size of \emph{d\textsubscript{+}} = 0.45.\textsuperscript{4}
Moreover it is known that ER strategies reduce physiological arousal, measured via electromyography (EMG) in the region of the \emph{corrugator supercilii}.\textsuperscript{5}
So these tactics from three different strategies proved to be effective in the short term.
However, in order to be able to make a statement on their general benefit, longer-term consequences must also be considered.
Especially strategies that do not put the emotional content of the situation into a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
Long-term consequences of subjectively reported habitual use of emotion regulation strategies for affect and well-being have been discussed.\textsuperscript{6}
Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the assumption of \emph{adaptive} and \emph{maladaptive} strategies.
For example, it could be shown that maladaptive ER strategies mediate the effect between neuroticism and depressive symptoms.\textsuperscript{7}
Also, a number of ER strategies is linked to psychological disorders (for meta-analytic review, see Aldao et al.).\textsuperscript{8}

The postulation of \emph{adaptive} and \emph{maladaptive} strategies was put in a new perspective with the concept of ER flexibility.
Similar to other psychological domains, e.g., attention and goal pursuit, \emph{maladaptive} now refers to inflexible strategy use or use of strategies that are hindering the achievement of goals.\textsuperscript{9}
Adaptive flexible ER requires having a large repertoire of ER strategies.\textsuperscript{9}
For example, greater ER variability is related to reduced negative affect and therefore beneficial in daily life.\textsuperscript{10}
Strategies have to be chosen from the repertoire that are useful for goal achieving.
Evidence from other contexts (e.g., intertemporal choice,)\textsuperscript{11} shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made.
Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs.
For example, it was shown that the intensity of a stimulus or situation plays a role in the choice.\textsuperscript{12}
Higher intensity of the stimulus leads to a choice of rather disengaging strategies, like distraction.\textsuperscript{12,13}
Further influencing factors are for example extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort.\textsuperscript{13,14}
Especially for effort, in our previous work we could show that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy.\textsuperscript{14}
In this study, participants used the strategies distancing and suppression while inspecting emotional pictures.
Afterwards they could choose, which strategy they want to use again.
Participants tended to re-apply the strategy that was subjectively less effortful, even though it was subjectively not the most effective one - in this case: suppression.
Interestingly, the choice was independent of self reported habitual use of suppression and reappraisal.
What has been missing in research on ER choice so far is information regarding the strategy \emph{not} chosen.
People choose a strategy that they prefer for different, relatively well-known reasons.
However, nothing is revealed about the strategy that is \emph{not chosen}.

The postulation of \emph{adaptive} and \emph{maladaptive} strategies was put into a new perspective with the concept of ER flexibility.
Similar to other psychological domains such as attention and goal pursuit, \emph{maladaptive} now refers to inflexible strategy use or the use of strategies that are hindering the achievement of goals.\textsuperscript{9}
In contrast, \emph{adaptive} ER requires having a large repertoire of ER strategies to choose from\textsuperscript{9} and choosing the strategy that is useful for goal achievement in a particular situation.
This greater ER variability has been shown to be related to reduced negative affect.\textsuperscript{10}
The process of choosing an ER strategy from one's own repertoire likely shares similarities with other contexts such as intertemporal choice, in which individuals assign subjective values to every choice option.\textsuperscript{11}
Additionally, there are ER-specific influences on choice behaviour such as the intensity of the stimulus or situation, which leads to a choice of rather disengaging strategies like distraction, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort.\textsuperscript{13,14}
Effort in particular appeared to be the main factor in ER choice behaviour in our previous work.\textsuperscript{14}
In that study, participants used the strategies distancing and suppression while inspecting emotional pictures, and could choose which strategy they wanted to use again.
Participants tended to re-apply the strategy that was less effortful, even though it was not the most effective one for them - in this case: Suppression.
Interestingly, the choice was independent of self reported habitual use of suppression and reappraisal.
Research on ER choice has shown that individuals choose a strategy that they prefer for different, relatively well-known reasons.
However, nothing has been investigated regarding the strategy that is \emph{not} chosen.

We assume that people choose the strategy that has the highest value for them at that moment.
The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement.\textsuperscript{9}
One certainly central goal is the regulation of negative affect.
A second, intrinsic and rather less obvious goal is the avoidance of effort.\textsuperscript{15}
When given the choice, most individuals prefer tasks that are less effortful.\textsuperscript{16}
We assume that both aspects are traded off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal \emph{and} is less effortful.
SVs of ER Strategies could be helpful to describe the ER repertoire\textsuperscript{9} more comprehensively.
Depending on the flexibility of a person, different patterns of SVs could be conceivable: A person with high flexibility would show relatively high SVs for a number of strategies.
This would mean that all strategies are a good option for goal achievement.
A second person with less flexibilty, however, would show high SVs only for one strategy, or for no strategy at all.
This in turn would mean that no strategy is a good choice to achieve ER goals.

@@

In the original study by Westbrook et al.,\textsuperscript{17} cognitive load was varied using the \emph{n}-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli.
Participants had to decide in an iterative procedure whether they wanted to repeat a higher \emph{n}-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward, with the implicit assumption taht teh objectively easiest \emph{n}-back level has the highest SV.
In the current study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: We have to adapt the assumption that the easiest \emph{n}-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies.\textsuperscript{14}
Moreover, there is nothing like an objectively easiest ER strategy.
Therefore, we have to add an additional step, which preceeds the other steps and where the option with the higher subjective value is determined.
In this step, the same monetary value (i.e., 1 €) is assigned to both options.
The assumption is that participants now choose the option that has the higher SV for them.
In the next step we return to the original paradigm.
The higher monetary value (i.e., 2 €) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
In the following steps, the lower value is changed in every iteration according to Westbrook et al.\textsuperscript{17} until the indifference point is reached.
This procedure will be repeated until all strategies have been compared.
The SV of each strategy is calculated as the mean of this strategy's SV from all comparisons.
In case a participant has a clear preference for one strategy, the SV of this strategy will be 1.
But our paradigm can also account for the case that a person does not have a clear preference.
Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see figure 1).
Additionally, we will test our adapted paradigm in a \emph{n}-back task and explore whether this paradigm can describe individuals that do not prefer the easiest \emph{n}-back option (see Zerna et al., \ldots).

\begin{figure}
\includegraphics[width=0.98\linewidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CERED/99_Thinktank/Other/Paradigm_Scheme_T2} \caption{Exemplary visualization of two response patterns. In the top half, the person has a clear preference for one of the three strategies. In the lower half, they have no clear preference and therefore show an inconsistent response pattern. This pattern can also be represented by our paradigm.}\label{fig:fig1}
\end{figure}

\hypertarget{the-present-study}{%
\subsection{1.2 The present study}\label{the-present-study}}

The aim of the present study is to evaluate if this paradigm is suitable for determining SVs of ER strategies.
As a manipulation check, we want to explore whether ER strategies distraction, distancing, and suppression effectively reduce emotional arousal and require cognitive effort. The following hypotheses are proposed for this purpose:

\begin{itemize}
\tightlist
\item
  H1a) Subjective arousal (arousal ratings) is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
\item
  H1b) Physiological arousal (EMG \emph{corrugator} activity) is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
\item
  H1c) Physiological arousal (EMG \emph{levator} activity) is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
\item
  H2a) Subjective effort (effort ratings) is greater after using an Er strategy (distraction, distancing, suppression) compared to active viewing.
\item
  H2b) The majority of participants ruse the strategy that was least effortful for them.
\end{itemize}

Further we want to explore which variables predict individual subjective values of ER strategies and whether effort is the best predictor for SVs of ER strategies with the following hypotheses:

\begin{itemize}
\tightlist
\item
  H3a) Subjective effort ratings negatively predict SVs of ER strategies.
\item
  H3b) Subjective arousal ratings negatively predict SVs of ER strategies.
\item
  H3c) EMG \emph{corrugator} activity negatively predict SVs of ER strategies.
\item
  H3d) EMG \emph{levator} activity negatively predict SVs of ER strategies.
\item
  H4a) SVs decline with increasing effort, even after controlling for task performance measured by subjective arousal ratings, \emph{corrugator} and \emph{levator} activity.
\end{itemize}

We also want to explore whether SVs are related to flexible emotion regulation:

\begin{itemize}
\tightlist
\item
  H5a) The higher the SV, the more likely the respective strategy is chosen.
\item
  H5b) SVs are lower and decline stronger when ER flexibility is lower.
\end{itemize}

@@

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.\textsuperscript{18}
The paradigm was written and presented using \emph{Psychopy}.\textsuperscript{19}
We used \emph{R} with \emph{R Studio}\textsuperscript{20,21} with the main packages \emph{afex}\textsuperscript{22} and \emph{BayesFactor}\textsuperscript{23} for all analyses.
The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at \url{https://github.com/ChScheffel/CERED}.
A complete list of all measures assessed in the study can be found at OSF (\url{https://osf.io/vnj8x/}) and GitHub (\url{https://github.com/ChScheffel/CERED}).

@@

The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK\ldots).
Prior to testing, written informed consent will be obtained.
Participants will receive 30€ in total or course credit for participation.

@@

The procedure described above was tested in a pilot study with \(N=16\) participants (9 female; age: \(M = 24.1\text{ }\pm\text{ }SD = 3.6\)).
Results showed significant higher subjective arousal for active viewing of negative pictures, compared to active viewing of neutral pictures.
ER strategies did not lead to a reduction of subjective arousal compared to active viewing of negative pictures.
However, ER strategies were associated with reduced facial muscle activity of the \emph{corrugator} and \emph{levator} compared to active viewing of negative pictures.
Yet we found in accordance with our previous studies\textsuperscript{14} that the use of ER strategies compared to active viewing was associated with increased subjective effort.

@@

Young, healthy participants (aged 18 to 30 years) will be recruited using the software \emph{ORSEE}\textsuperscript{24} at the Technische Universität Dresden.
Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
Participants will be invited to compete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
The study consists of two lab sessions, which take place in a shielded cabin with constant lighting.
Before each session, participants receive information about the respective experimental procedure and provide informed consent.
At the beginning of the first session participants fill out a demographic questionnaire and complete an n-Back task with the levels one to four.
Then, they complete an effort discounting (ED) procedure on screen, followed by a random repetition of one n-back level.
The second session, containing the ER paradigm, takes place exactly one week after session one.
Participants provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
A brief training ensures that all participants are able to implement the ER strategies.
Next, electrodes to measure EMG being attached and the ER paradigm is conducted.
Participants receive 30.00€ or course credit as compensation.
Study data are being collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden.\textsuperscript{25,26}

@@

The online survey contains a number of questionnaires: General psychological well-being is assessed using the German version of the WHO-5 scale.\textsuperscript{27,28}
To capture the construct of resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{31} is used.
Habitual use of ER is assessed using the German version of the Emotion Regulation Questionnaire (ERQ).\textsuperscript{6,32}
For the assessment of ER ability we use the Flexible Emotion Regulation Scale (FlexER).\textsuperscript{33}
Implicit theories of willpower in emotion control are assessed using the implicit theories questionnaire from.\textsuperscript{34}
To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{35,36} is used.
To assess self-control, sum scores of the German versions of the following questionnaires are used:\textsuperscript{37} the Self-Regulation Scale (SRS),\textsuperscript{38} the Brief Self-Control Scale (BSCS),\textsuperscript{39,40} and the Barratt Impulsiveness Scale (BIS-11).\textsuperscript{41,42}
Attentional control is assessed using the Attentional Control Scale (ACS).\textsuperscript{43}
For more detailed information on psychometric properties of the questionnaires, please see \protect\hyperlink{SupplementQuestionnaires}{supplementary material}.

@@

The ER paradigm roughly consists of three parts that will be described in the following.

\emph{Part one: ER task.} Part one is a standard ER task in a block design (see Figure X), similar to paradigms previously used by our group.\textsuperscript{14}
Participants are told to actively view neutral and negative pictures (see \protect\hyperlink{ux5cux23stimuli}{2.3.3}) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
Every participant first has the condition ``active viewing-neutral'' that serves as a baseline condition.
During this block, 20 neutral pictures are presented.
Participants are asked to ``actively view all pictures and permit all emotions that may arise.'' In the second block, participants actively viewe negative pictures.
During the third, fourth, and fifth block, participants see negative pictures and are asked to regulate their emotions using distraction, distancing, and suppression.
In order to achieve distraction, participants are asked to think of a geometric object or an everyday activity, like brushing their teeth.
During distancing, participants are asked to ``take the position of a non-involved observer, thinking about the picture in a neutral way.'' Participants are told not to re-interpret the situation or attaching a different meaning to the situation.
During suppression, participants are told to ``suppress their emotional facial expression.'' They should imagine being observed by a third person that should not be able to tell just by looking at the facial expression whether the person is looking at an emotional picture.
Participants are instructed not to suppress their thoughts or change their facial expression to the opposite.\textsuperscript{14}
All participants receive written instruction and complete a training session.
After the training session, participants are asked about their applied ER strategies to avoid misapplication.
The order of the three regulation blocks (distraction, distancing, and suppression) is randomized between participants.

>>>>

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Subjective values of emotion regulation strategies}
\keywords{emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis\newline\indent Word count: 139}
\usepackage{lineno}

@@

\abstract{
Individuals have a repertoire of emotion regulation (ER) strategies at their disposal, which they can use more or less flexibly.
In ER flexibility research, strategies that facilitate goal achievement are considered adaptive and therefore are subjectively valuable.
Individuals are motivated to reduce their emotional arousal effectively and to avoid cognitive effort.
Perceived costs of ER strategies in the form of effort, however, are highly subjective.
Subjective values (SVs) should therefore represent a trade-off between effectiveness and subjectively required cognitive effort.
However, SVs of ER strategies have not been determined so far.
We present a paradigm that is suitable for determining individual SVs of ER strategies.
Using a multilevel modelling approach, it will be investigated whether individual SVs can be explained by effectiveness (subjective arousal, facial muscle activity) and subjective effort.
Relations of SVs to personality traits will be explored.
}

@@

Every day we are confronted with stressful or emotionally demanding situations.
The ability to modify emotional experiences, expressions, and physiological reactions\textsuperscript{1} to regulate emotions is an important cognitive skill.
It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning.\textsuperscript{2}
Different strategies can be used to regulate emotions, namely situation selection, situation modification, attentional deployment, cognitive change, and response modification,\textsuperscript{1} and, following the taxonomy of Powers and LaBar,\textsuperscript{3} individuals can implement ER strategies by means of different tactics.
So called antecedent-focused strategies, e.g., attentional deployment and cognitive change, take effect early in the emotion generation process.\textsuperscript{1}
In contrast, response modification takes place late in the process and is therefore conceptualized as a response-focused strategy.\textsuperscript{1}
This postulated temporal sequence of ER strategies influences their effectiveness.
It is meta-analytically proven that all mentioned strategies reduce subjective emotional arousal.\textsuperscript{4}
Distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed small to medium effect sizes on measures of emotional experience (distraction: \emph{d\textsubscript{+}} = 0.27; suppression: \emph{d\textsubscript{+}} = 0.27).
Distancing as tactic of cognitive change showed the highest effectiveness with an effect size of \emph{d\textsubscript{+}} = 0.45.\textsuperscript{4}
Moreover, it is known that ER strategies reduce physiological responses of emotions, especially emotional valence as measured via facial electromyography (EMG)\textsuperscript{5} .
So these tactics from three different strategies proved to be effective in the short term.
However, in order to be able to make a statement on their general benefit, longer-term consequences must also be considered.
In particular, strategies that do not put the emotional content of the situation into a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
Longer lasting consequences of self-reported habitual use of ER strategies for affect and well-being have been discussed.\textsuperscript{6}
Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the postulation of \emph{adaptive} and \emph{maladaptive} ER strategies.
For example, it was shown that maladaptive ER strategies mediate the effect between neuroticism and depressive symptoms.\textsuperscript{7}
In addition, a number of ER strategies have been associated with mental disorders (for meta-analytic review, see Aldao et al.).\textsuperscript{8}

The postulation of \emph{adaptive} and \emph{maladaptive} ER strategies was put in a new perspective with the concept of ER flexibility.
Similar to other psychological domains, e.g., attention and goal pursuit, \emph{maladaptive} now refers to inflexible ER strategy use or use of strategies that are hindering goal achievement.\textsuperscript{9}
Adaptive flexible ER requires a large repertoire of ER strategies.\textsuperscript{9}
For example, greater ER flexibility is related to reduced negative affect and therefore beneficial in daily life.\textsuperscript{10}
Strategies have to be chosen from the repertoire that are useful for goal achieving.
Evidence from other contexts (e.g., intertemporal choice,)\textsuperscript{11} shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made.
Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs.
For example, it was shown that the intensity of a stimulus or situation plays a role in the choice.\textsuperscript{12}
Higher intensity of the stimulus leads to a choice of rather disengaging strategies, like distraction.\textsuperscript{12,13}
Further influencing factors are for example extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort.\textsuperscript{13,14}
Especially for effort, in our previous work we could show that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy.\textsuperscript{14}
In this study, participants used the strategies distancing and suppression while inspecting emotional pictures.
Afterwards, they choose which strategy they wanted to use again.
Participants tended to re-apply the strategy that was subjectively less effortful, even though it was subjectively not the most effective one - in this case: suppression.
Interestingly, the choice was independent of self-reported habitual use of suppression and reappraisal.
What has been missing in research on ER choice so far is information regarding the strategy \emph{not} chosen.
People choose a strategy that they prefer for different, relatively well-known reasons.
However, nothing is revealed about the strategy that is \emph{not chosen}.

We assume that people choose the strategy that has the highest value for them at the moment.
The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement.\textsuperscript{9}
One certainly central goal is the regulation of negative affect.
A second, intrinsic and less obvious goal is the avoidance of effort.\textsuperscript{15}
When given the choice, most individuals prefer tasks that are less effortful.\textsuperscript{16}
We assume that both aspects are traded off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal \emph{and} is less effortful.
SVs of ER Strategies could be helpful to describe the ER repertoire\textsuperscript{9} more comprehensively.
Depending on the flexibility of a person, different patterns of SVs could be conceivable: A person with high flexibility would show relatively high SVs for a number of strategies.
This would mean that all strategies are a good option for goal achievement.
A second person with less flexibilty, however, would show high SVs only for one strategy, or for no strategy at all.
This in turn would mean that no strategy is a good choice to achieve ER goals.

@@

In the original study by Westbrook et al.,\textsuperscript{17} cognitive load was varied using the \emph{n}-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli.
Participants had to decide in an iterative procedure whether they wanted to repeat a higher \emph{n}-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward, with the implicit assumption that the objectively easiest \emph{n}-back level has the highest SV.
In the present study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: We have to adapt the assumption that the easiest \emph{n}-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies.\textsuperscript{14}
Moreover, there is nothing like an objectively easiest ER strategy.
Therefore, we have to add an additional step, which preceeds the other steps and where the option with the higher subjective value is determined.
In this step, the same monetary value (i.e., 1 €) is assigned to both options.
The assumption is that participants now choose the option that has the higher SV for them.
In the next step we return to the original paradigm.
The higher monetary value (i.e., 2 €) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
In the following steps, the lower value is changed in every iteration according to Westbrook et al.\textsuperscript{17} until the indifference point is reached.
This procedure will be repeated until all strategies have been compared.
The SV of each strategy is calculated as the mean of this strategy's SV from all comparisons.
In case a participant has a clear preference for one strategy, the SV of this strategy will be 1.
But our paradigm can also account for the case that a person does not have a clear preference.
Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see Figure \ref{fig:ResponsePatterns}).
Additionally, we will test our adapted paradigm in a \emph{n}-back task and explore whether this paradigm can describe individuals that do not prefer the easiest \emph{n}-back option (see Zerna et al., \ldots).

\begin{figure}
\includegraphics[width=\textwidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CERED/06_Paper/ER-ED/figures/Paradigm_Scheme_T2} \caption{Exemplary visualization of two response patterns. In the top half, the person has a clear preference for one of the three strategies. In the lower half, they have no clear preference and therefore show an inconsistent response pattern. This pattern can be represented by our paradigm.}\label{fig:ResponsePatterns}
\end{figure}

The aim of the present study is to evaluate whether this paradigm is suitable for determining SVs of ER strategies.
As a manipulation check, we want to investigate whether the ER strategies distraction, distancing, and suppression effectively reduce emotional arousal and physiological responses as well as whether they require cognitive effort.
The following hypotheses are proposed:

\begin{itemize}
\tightlist
\item
  H1a) Subjective arousal (arousal ratings) is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
\item
  H2a) Physiological responses in facial EMG that is sensitive to negative emotion (\emph{corrugator} activity) are lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
\item
  H2b) Physiological responses in facial EMG that is sensitive to negative emotion (\emph{levator} activity) are lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
\item
  H3a) Subjective effort (effort ratings) is greater after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
\item
  H3b) The majority of participants re-uses the strategy that was least effortful for them.
\end{itemize}

Furthermore, we want to investigate whether the following variables predict individual subjective values of ER strategies and whether effort is the best predictor for SVs of ER strategies with the following hypotheses:

\begin{itemize}
\tightlist
\item
  H4a) Subjective effort ratings negatively predict SVs of ER strategies.
\item
  H4b) Subjective arousal ratings negatively predict SVs of ER strategies.
\item
  H4c) EMG \emph{corrugator} activity negatively predicts SVs of ER strategies.
\item
  H4d) EMG \emph{levator} activity negatively predicts SVs of ER strategies.
\item
  H5a) SVs decline with increasing effort, even after controlling for task performance measured by subjective arousal ratings, \emph{corrugator} and \emph{levator} activity.
\end{itemize}

We also want to investigate whether SVs are related to flexible emotion regulation:

\begin{itemize}
\tightlist
\item
  H6a) The higher the SV, the more likely the respective strategy is chosen.
\item
  H6b) SVs are lower and decline stronger when ER flexibility is lower.
\end{itemize}

@@

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.\textsuperscript{18}
The paradigm was written and presented using \emph{PsychoPy}.\textsuperscript{19}
We used \emph{R} with \emph{R Studio}\textsuperscript{20,21} with the main packages \emph{afex}\textsuperscript{22} and \emph{BayesFactor}\textsuperscript{23} for all analyses.
The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at \url{https://github.com/ChScheffel/CERED}.
A complete list of all measures assessed in the study can be found at OSF (\url{https://osf.io/vnj8x/}) and GitHub (\url{https://github.com/ChScheffel/CERED}).

@@

The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK\ldots).
Prior to testing, written informed consent will be obtained.
Participants will receive 30 € in total or course credit for participation.

@@

The newly developed ER paradigm was tested in a pilot study with \(N=16\) participants (9 female; age: \(M = 24.1\text{ }\pm\text{ }SD = 3.6\)).
Regarding self-reported arousal, results showed significant higher subjective arousal for active viewing of negative compared to neutral pictures.
However, ER strategies did not lead to a reduction of subjective arousal compared to active viewing of negative pictures.
Regarding physiological responses, ER strategies were associated with reduced facial muscle activity of the \emph{corrugator} and \emph{levator} compared to active viewing of negative pictures.
In accordance with our previous study,\textsuperscript{14} we found that the use of ER strategies compared to active viewing was associated with increased subjective effort.
All results are detailed in the \protect\hyperlink{SupplementaryMaterial}{Supplementary Material}

@@

Young healthy participants (aged 18 to 30 years) will be recruited using the software \emph{ORSEE}\textsuperscript{24} at the Technische Universität Dresden.
Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
Participants will be invited to complete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
The study consists of two lab sessions, which will take place in a shielded cabin with constant lighting.
Before each session, participants will receive information about the respective experimental procedure and provide informed consent.
At the beginning of the first session participants will fill out a demographic questionnaire and complete an n-back task with the levels one to four.
Then, they will complete an effort discounting (ED) procedure on screen, followed by a random repetition of one n-back level.
The second session will comprise the ER paradigm and take place exactly one week after session one.
Participants will provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
A brief training will ensure that all participants are able to implement the ER strategies.
Next, electrodes to measure facial EMG will be attached and the ER paradigm will be conducted.
Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden.\textsuperscript{25,26}

@@

The online survey will contain a number of questionnaires: General psychological well-being will be assessed using the German version of the WHO-5 scale.\textsuperscript{27,28}
To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{31} will be used.
Habitual use of ER will be assessed using the German version of the Emotion Regulation Questionnaire (ERQ).\textsuperscript{6,32}
For the assessment of ER flexibility we will use the Flexible Emotion Regulation Scale (FlexER).\textsuperscript{33}
Implicit theories of willpower in emotion control will be assessed using the implicit theories questionnaire from.\textsuperscript{34}
To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{35,36} will be used.
To assess self-control,\textsuperscript{37} sum scores of the German versions of the following questionnaires will be used: the Self-Regulation Scale (SRS),\textsuperscript{38} the Brief Self-Control Scale (BSCS),\textsuperscript{39,40} and the Barratt Impulsiveness Scale (BIS-11).\textsuperscript{41,42}
Attentional control will be assessed using the Attentional Control Scale (ACS).\textsuperscript{43}
For more detailed information on psychometric properties of the questionnaires, please see \protect\hyperlink{SupplementQuestionnaires}{supplementary material}.

@@

The ER paradigm will consist of three parts that will be described in the following.

\emph{Part one: ER task.} Part one will be a standard ER task in a block design (see Figure \ref{fig:DesignERED}), similar to paradigms previously used by our group.\textsuperscript{14}
Participants will be told to actively view neutral and negative pictures (see \protect\hyperlink{ux5cux23stimuli}{2.3.3}) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
Every participant first will have the condition ``active viewing-neutral'' that serves as a baseline condition.
During this block, 20 neutral pictures will be presented.
Participants will be asked to ``actively view all pictures and permit all emotions that may arise.''
In the second block, participants will actively view negative pictures.
During the third, fourth, and fifth block, participants will see negative pictures and will be asked to regulate their emotions using distraction, distancing, and suppression.
In order to achieve distraction, participants will be asked to think of a geometric object or an everyday activity, like brushing their teeth.
During distancing, participants will be asked to ``take the position of a non-involved observer, thinking about the picture in a neutral way.''
Participants will be told not to re-interpret the situation or attaching a different meaning to the situation.
During suppression, participants will be told to ``suppress their emotional facial expression.''
They should imagine being observed by a third person that should not be able to tell by looking at the facial expression whether the person is looking at an emotional picture.
Participants will be instructed not to suppress their thoughts or change their facial expression to the opposite.\textsuperscript{14}
All participants will receive written instruction and complete a training session.
After the training session, participants will be asked about their applied ER strategies to avoid misapplication.
The order of the three regulation blocks (distraction, distancing, and suppression) will be randomized between participants.

\emph{Part two: ER effort discounting.} In the second part, ER effort discounting will take place.
The procedure of the discounting will follow the COG-ED paradigm by Westbrook et al.\textsuperscript{17} with a major change.
We will use the following adaption that allows the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.~distancing, distraction vs.~suppression, and distancing vs.~suppression), two strategies with monetary values will be presented.
The order of the comparisons will be randomized.
Because there is no strategy that is objectively more difficult, we will add an initial comparison that begins with the option ``1 € for strategy A or 1 € for strategy B''.
The strategy that is not chosen will be assigned the value of 2 €.
From this point on, comparisons between strategies will follow the original COG-ED paradigm.\textsuperscript{17}
Participants will be instructed to decide as realistically as possible by imagining that the money displayed is actually available for choice.

\emph{Part three: ER choice.} After the discounting part, participants will choose which of the three ER strategies (distraction, distancing or suppression) they want to re-apply.
Importantly, there will be no further instruction on what basis they should make their decision.
Participants should make their decision freely, according to criteria they consider important for themselves.
However, participants will be asked to state the reasons for the decision afterwards.
As soon as they have decided, they will see the respective instruction and the block with another 20 negative pictures starts.
